---
title: "Causal Inference using DiD and Bayesian time series approach"
author: "Guyi Zhou, Naman Shukla"
date: "12/11/2020"
output:
  html_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#import required libraries
```{r message = FALSE}
library(readxl)
library(dplyr)
library(tidyverse)
library(lubridate)
library(ggplot2)
library(stargazer)
```

#import data
```{r}
Data= read_excel("Data.xlsx", sheet = "Combined")
names(Data)
```

#Create a dummy variable to identify the group exposed to the treatment. Here countries with code USA were treated (=1). Other countries not envolved in the trade war between U.S & China are controlled for (=0).

```{r message = FALSE}
table(`Current ISO Country Code - Incorporation`)
Data$USA = ifelse(Data$`Current ISO Country Code - Incorporation` =="USA", 1, 0)
Data$Post = ifelse(Data$`Data Date` > "2018-07-06", 1, 0)
table(Data$USA)
```

#Create subset data for each control regions
```{r message = FALSE}
ausdata=subset(Data,Data$`Current ISO Country Code - Incorporation` =="USA" |Data$`Current ISO Country Code - Incorporation` =="AUS")
twdata=subset(Data,Data$`Current ISO Country Code - Incorporation` =="USA" |Data$`Current ISO Country Code - Incorporation` =="TWN")
kordata=subset(Data,Data$`Current ISO Country Code - Incorporation` =="USA" |Data$`Current ISO Country Code - Incorporation` =="KOR")
usadata=subset(Data,Data$`Current ISO Country Code - Incorporation` =="USA")
ausonly=subset(Data,Data$`Current ISO Country Code - Incorporation`  =="AUS")
```

#check length of dataframes if needed
```{r}
#length(unique(Data$`Global Company Key`[Data$`Current ISO Country Code - Incorporation` =="AUS"]))

#length(unique(Data$`Global Company Key`[Data$`Current ISO Country Code - Incorporation` =="TWN"]))

#length(unique(Data$`Global Company Key`[Data$`Current ISO Country Code - Incorporation` =="KOR"]))

#length(unique(Data$`Global Company Key`[Data$`Current ISO Country Code - Incorporation` =="USA"]))
```

#Linear Regression Model
```{r}
model=lm(ROA~Post,usadata)
summary(model)
stargazer(model, type='text')
```

# Descriptive Analysis and Parallel Trend Check
```{r message = FALSE}

parallelroe=function(Data){
attach(Data)
date1=as.character(`Data Date`)
agg_data <- aggregate(ROE~ date1 +USA,Data,mean)
agg_data$treatment <- as.factor(agg_data$USA)
agg_data$date1 <- ymd(agg_data$date1 )

# Basic line plot with points
library(ggplot2)
ggplot(data=agg_data, aes(x=date1, y=ROE, group=treatment)) + geom_line(aes(linetype=treatment, color=treatment))+geom_point(aes(color=treatment))+theme(legend.position="top")+
 geom_vline(xintercept = as.numeric(as.Date("2018-07-06")))}

parallelroa=function(Data){
attach(Data)
date1=as.character(`Data Date`)
agg_data <- aggregate(ROA~ date1 +USA,Data,mean)
agg_data$treatment <- as.factor(agg_data$USA)
agg_data$date1 <- ymd(agg_data$date1 )

# Basic line plot with points
library(ggplot2)
ggplot(data=agg_data, aes(x=date1, y=ROA, group=treatment)) + geom_line(aes(linetype=treatment, color=treatment))+geom_point(aes(color=treatment))+theme(legend.position="top")+
 geom_vline(xintercept = as.numeric(as.Date("2018-07-06")))}

parallelgpm=function(Data){
attach(Data)
date1=as.character(`Data Date`)
agg_data <- aggregate(GPM~ date1 +USA,Data,mean)
agg_data$treatment <- as.factor(agg_data$USA)
agg_data$date1 <- ymd(agg_data$date1 )

# Basic line plot with points
library(ggplot2)
ggplot(data=agg_data, aes(x=date1, y=GPM, group=treatment)) + geom_line(aes(linetype=treatment, color=treatment))+geom_point(aes(color=treatment))+theme(legend.position="top")+
 geom_vline(xintercept = as.numeric(as.Date("2018-07-06")))}

```

#Check the parallel trend for Control Group (Australia,Taiwan & Korea )
```{r message = FALSE}
parallelroa(Data)
parallelroe(Data)
parallelgpm(Data)
par(mfrow=c(2,2))
```

#Check the parallel trend for Control Group (Australia )
```{r message = FALSE}
parallelroa(ausdata)
parallelroe(ausdata)
parallelgpm(ausdata)
```

#Check the parallel trend for Control Group (Taiwan )
```{r message = FALSE}
parallelroa(twdata)
parallelroe(twdata)
parallelgpm(twdata)
```

#Check the parallel trend for Control Group (Korea)
```{r message = FALSE}
parallelroa(kordata)
parallelroe(kordata)
parallelgpm(kordata)
```

# Differnece in Difference Model
Create an interaction between time and traedwar, which is the difference. 
```{r message = FALSE}
attach(ausdata)
model=lm(ROA~USA*Post,ausdata)
summary(model)
stargazer(model, type='text')
```

#DiD at Industry level 
```{r message = FALSE}
attach(ausdata)
unique(`GIC Sectors`)
industry.ROA=function(a){
  data1=subset(ausdata,`GIC Sectors`==a)
  model=lm(ROA~USA*Post,data1)
  return(stargazer(model, type='text'))
}

```

```{r message = FALSE}
attach(ausdata)
industry.ROA(25)#Consumer Discretionary
industry.ROA(45)#Information Technology
industry.ROA(30)#Consumer Staples
industry.ROA(35)#Health Care
industry.ROA(15)#Materials
industry.ROA(10)#Energy
industry.ROA(20)#Industrials
industry.ROA(50)#Communication Services
industry.ROA(40)#Financials
industry.ROA(55)#Utilities
industry.ROA(60)#Real Estate
```

#fitting bayesian model to address limiations of DiD approach as discussed in Read.md.

```{r}
#create time points
time.points<-seq.Date(as.Date("2016-03-31"),by = "quarter", length.out=16)
```

```{r}
#declare time series variables
US_ROA <-ts(usadata$ROA)
Control_ROA <-ts(ausonly$ROA)

#bind data in one dataframe
data <-zoo(cbind(US_ROA,Control_ROA),time.points)
```


#import CI package
```{r}
library(CausalImpact)
```

```{r}
#define intervention period here
pre.period <-as.Date(c("2016-03-31","2018-07-31"))
post.period <-as.Date(c("2018-08-01","2019-12-31"))
```

```{r}
#fit the causal impact model based on bayesian time series approach
impact_overall <-CausalImpact(data, pre.period, post.period)
plot(impact_overall)
summary(impact_overall)
```

#function to wrangle data to measure impact by industries.
```{r}
industry.ROA_CI=function(a){
  data1 = filter(usadata, usadata$'GIC Sectors' == a)
  data_ctrl = filter(ausonly, ausonly$'GIC Sectors' == a)
  US_GIC_ROA <-ts(data1$ROA)
  US_Control_ROA <-ts(data_ctrl$ROA)
  data_sector <-na.trim(zoo(cbind(US_GIC_ROA,US_Control_ROA),time.points))
  impact <-CausalImpact(data_sector, pre.period, post.period)
  summary(impact)
  return(plot(impact))
}
```


```{r}
industry.ROA_CI(25)#Consumer Discretionary
industry.ROA_CI(45)#Information Technology
industry.ROA_CI(30)#Consumer Staples
industry.ROA_CI(35)#Health Care
industry.ROA_CI(15)#Materials
industry.ROA_CI(10)#Energy
industry.ROA_CI(20)#Industrials
industry.ROA_CI(50)#Communication Services
industry.ROA_CI(40)#Financials
industry.ROA_CI(55)#Utilities
industry.ROA_CI(60)#Real Estate
```


